Inefficient Concessions and Mediation

### 2023-08-06 draft_narrow.tex
Update draft_narrow.tex
Update the description of why we define welfare the way we do.

Parameters are common knowledge with the exception of $\delta_i$, which is country $i$'s private information. We will take the measure of social welfare, and thus the determinant of the optimal equilibrium, to be the sum of participating high types' expected utilities.

>>>>

Parameters are common knowledge with the exception of $\delta_i$, which is country $i$'s private information. We take achieving peace, or more broadly, achieving the provision of public goods, as the normative goal with respect to advancing social welfare. Only high types are capable of making peace/providing public goods, and thus we will take as the measure of social welfare to be the sum of the participating high types’ utilities.
